High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-11 paper.tex
added "\\"
A bit more space saving
Author list refine.

\title{High-Throughput Computing on High-Performance Platforms: A Case Study}

@@

\author{
    \IEEEauthorblockN{
        Alessio Angius\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
        Danila Oleynik\IEEEauthorrefmark{1}\IEEEauthorrefmark{5},
        Sergey Panitkin\IEEEauthorrefmark{1}\IEEEauthorrefmark{4},
        Matteo Turilli\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},\\
        Kaushik De\IEEEauthorrefmark{5},
        Alexei Klimentov\IEEEauthorrefmark{4},
        Sarp Oral\IEEEauthorrefmark{6},
        Jack C. Wells\IEEEauthorrefmark{7} and
        Shantenu Jha\IEEEauthorrefmark{2}
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{1}First authors, alphabetical order
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{2}Department of Electric and Computer Engineering, Rutgers University, NJ, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{4}Physics Department, Brookhaven National Laboratory, NY, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{5}Physics Department, University of Texas Arlington, TX, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{6}Oak Ridge Leadership Computing Facility, Oak Ridge National Laboratory, TN, USA
        }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{7}National Center for Computational Sciences, Oak Ridge National Laboratory, TN, USA
        }
}

@@

\ifreview
General comments to address:
\begin{itemize}
    \color{red} 
    % \item REVIEWER 1: There is a problem with capitalization in some
    % reference titles, ie. [2], [3], [4], [7], [8], [9], [10], [11], [12],
    % [13]. Reference [6] is just an author list, year and title. Should there
    % be more here?\mtnote{Fixed.}
    \item REVIEWER 2:  Key concepts such as pilot jobs, tasks and workloads
    are not meaningfully defined.
    % \item REVIEWER 2: the information provided is insufficient to asses in
    % how far any of the presented evaluation, characterization or lessons are
    % applicable outside of TITAN and PanDA Broker combined.
    % \item REVIEWER 2: Several references are of poor quality. For example,
    % [19] is a slide collection even though there are many papers for the
    % referenced work.\mtnote{Reference [19] is a technical paper.}
    % \item REVIEWER 3: Title looks too general for what amounts to the
    % implementation of an adapter component in a system that is very specific
    % to a single HEP experiment. (In general, title, abstract and conclusions
    % seem to over-state the contributions of this paper, considering this is a
    % general eScience conference and not a WLCG-specific one.)
\end{itemize}
\fi

>>>>

\title{High-Throughput Computing on \\ High-Performance Platforms: A Case Study}

@@

\author{
    \IEEEauthorblockN{
        Danila Oleynik\IEEEauthorrefmark{1}\IEEEauthorrefmark{5},
        Sergey Panitkin\IEEEauthorrefmark{1}\IEEEauthorrefmark{4},
        Matteo Turilli\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},\\
        Alessio Angius\IEEEauthorrefmark{2},
        Sarp Oral\IEEEauthorrefmark{6},
        Kaushik De\IEEEauthorrefmark{5},
        Alexei Klimentov\IEEEauthorrefmark{4},
        Jack C. Wells\IEEEauthorrefmark{7} and
        Shantenu Jha\IEEEauthorrefmark{2}\IEEEauthorrefmark{3}
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{1}First authors, alphabetical order
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{2}Department of Electric and Computer Engineering, Rutgers University, NJ, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{3}Computational Science Initiative, Brookhaven National Laboratory, NY, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{4}Physics Department, Brookhaven National Laboratory, NY, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{5}Physics Department, University of Texas Arlington, TX, USA
    }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{6}Oak Ridge Leadership Computing Facility, Oak Ridge National Laboratory, TN, USA
        }
    \IEEEauthorblockA{
        \IEEEauthorrefmark{7}National Center for Computational Sciences, Oak Ridge National Laboratory, TN, USA
        }
}

@@

\ifreview
General comments to address:
\begin{itemize}
    \color{red} 
    % \item REVIEWER 1: There is a problem with capitalization in some
    % reference titles, ie. [2], [3], [4], [7], [8], [9], [10], [11], [12],
    % [13]. Reference [6] is just an author list, year and title. Should
    % there be more here?\mtnote{Fixed.}
    \item REVIEWER 2:  Key concepts such as pilot jobs, tasks and workloads
    are not meaningfully defined.    % \item REVIEWER 2: the information provided is insufficient to asses in
    % how far any of the presented evaluation, characterization or lessons
    % are applicable outside of TITAN and PanDA Broker combined.
    % \item REVIEWER 2: Several references are of poor quality. For example,
    % [19] is a slide collection even though there are many papers for the
    % referenced work.\mtnote{Reference [19] is a technical paper.}
    % \item REVIEWER 3: Title looks too general for what amounts to the
    % implementation of an adapter component in a system that is very
    % specific to a single HEP experiment. (In general, title, abstract and
    % conclusions seem to over-state the contributions of this paper,
    % considering this is a general eScience conference and not a
    % WLCG-specific one.)
\end{itemize}
\fi
